---
title: "Econometrics Group Assignment 1"
author: "Jon Ferrin"
date: "4/27/2020"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
```

  
```{r, include=FALSE}
library(mosaic)
library(pander)
library(readr)
library(plotly)
library(tidyverse)
library(car)
library(knitr)
library(ggplot2)
library(viridis)
library(ggsci)
```




```{r, error=FALSE, include=FALSE}
my_data2 <- read_csv('C:/Users/jscot/Documents/Econometrics_R/hprice2.csv')

my_data <- filter(my_data2, my_data2$median_price, my_data2$crime_per_capita, my_data2$rooms, my_data2$distance)

```

## Background
<style>
body {
text-align: justify}
</style>

This data analyzes the various factors that coudld go into a home purchase. The data includes: home prices, crimes committed per capita in the neighborhood, how much nitrous oxide is present on the site, average number of bedrooms per house, estimated distance to work, accessibility to radial highways, property taxes, student teacher ratio in the school districe, and the percentage of 'low status' people in the vicinity.  


```{r cars}
pander(summary(my_data))
```

Each of the graphics below were created to look for correlation between factors and median housing prices. 


```{r, error=FALSE, include=FALSE}
'pander(sd(my_data$median_price))
pander(sd(my_data$crime_per_capita))                  
pander(sd(my_data$distance))
pander(sd(my_data$rooms))'

'my_data_table1 <- matrix(c(sd(my_data$median_price), sd(my_data$crime_per_capita), sd(my_data$distance), sd(my_data$rooms)))

colnames(my_data_table1) <- c("Home $", "Distance", "Room")
rownames(my_data_table1) <- c("")
smoke <- matrix(c(51,43,22,92,28,21,68,22,9),ncol=3,byrow=TRUE)
> colnames(smoke) <- c("High","Low","Middle")
> rownames(smoke) <- c("current","former","never")
> smoke <- as.table(smoke)
> smoke
        High Low Middle
current   51  43     22
former    92  28     21
never     68  22      9'

```


```{r, echo=FALSE}
CrimePlot <- ggplot(data = my_data, aes(x = crime_per_capita, y = median_price, color=crime_per_capita))+
  geom_point()+
  labs( x= "Crime per Capita", y= "Home Prices", title = "House Prices vs Crime Rate")+
  scale_color_viridis()+
  theme_bw()
print(CrimePlot)
```

As we can see in Graph 1....

```{r, echo=FALSE}
RoomPlot <- ggplot(data = my_data, aes(x = rooms, y = median_price, color=rooms))+ 
  geom_point()+
  scale_color_viridis()+
  theme_bw()+
  labs(x="Number of Rooms", y="House Prices (Thousands)", title = "House Prices vs Number of Rooms")
print(RoomPlot)

```

As we can see in Graph 2....

```{r, echo=FALSE}
DistancePlot <- ggplot(data = my_data, aes(x = distance, y = median_price, color=distance))+ 
  geom_point()+
  scale_color_viridis()+
  theme_bw()+
  labs(x="Miles from Work", y="House Prices (Thousands)", title = "House Prices vs Miles to Work")
print(DistancePlot + ggtitle("Price vs Distance to Work"))

```

```{r}
layout(matrix(c(1,1,2,3), 2, 2, byrow = TRUE))
CrimePlot
RoomPlot
DistancePlot
```


